### 2015-02-23 paper_30_measure.tex
working on the quality element
reworked the end of chapter 2 moved stuff to Appendix A
working on Chapter 3

\section{MEASURING A SDO}

Anything can be measured \cite{Hubbard2010}.  An SDO
how numerous metrics.

A metric can be defined as the science of indirect measurement.
    The following are some examples of metrics that can be collected 
    about source code:
    \begin{itemize}
        \item SLOC - The number of Source Lines of Code 
        \item NOM - The Number of Methods per class
        \item Complexity - A numerical measure of the code complexity,
            some common examples are McCabe \cite{McCabe1976} and 
            Halstead \cite{Halstead1977}
        \item Design - The amount of coupling and cohesion present 
        in the software code
        \item Source Code Analysis - Tools that determine whether 
        code adheres to specified set of rules. Common 
        examples are PMD\footnote{PMD is a source code analysis product.  It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
    \end{itemize}

\subsection{INDICATORS}
Indicators can be crucial measurements
within any business setting, and an SDO is no exception. Determining
the correct indicators for an organization can
be difficult.  Software development organizations
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}

More information on the indicators can be found
in chapter 1 of \cite{parmenter2010}
as well as \cite{florac1999,kaplan1992}.

@@

It is important to note that software departments do not just
develop software.  The department has many other duties
including: deploying software, installing server hardware/software,
writing documentation, surveying users, and other things.

@@

>>>>

\section{EVALUATING AN SDO}

    Anything can be measured \cite{Hubbard2010}.  Thus, an SDO can be 
    measured.  Proper measurement is crucial for improvement because
    without a starting point it is impossible to determine progress.
    Also, consistent reporting is essential for 
    tracking historical performance.  Many methods are used
    to measure and evaluate SDOs.  Some of the common ones
    will be explained in this section.

    \subsection{METRICS}
        A \textit{metric} can be defined as the science of indirect measurement. Metrics
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
            \item NOM - The Number of Methods per class
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, around an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics is difficult.

    \subsection{INDICATORS}
        Indicators can be crucial measurements
        within any business setting, and an SDO is no exception. Determining
        the correct indicators for an organization can
        be difficult.  Software development organizations
        are no exception. 
        The differences between the indicators will be explored and
        possible measures for each indicator in an SDO will be
        presented.  Indicators are sometimes refered to as 
        performance measures \cite{parmenter2010}.  The four
        types of indicators important to an SDO are shown
        in Table \ref{tab:indicators}.

        \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Performance Measure}
                 & {\bfseries Description}\\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                \cmidrule[0.4pt](lr{0.125em}){2-2}%
                % \midrule
                \endhead

                RI (Result Indicator) & What has been done?   \\
                \myrowcolour%
                KRI (Key Result Indicator) & How you have done? \\
                PI (Performance Indicator) & What to do? \\
                \myrowcolour%
                KPI (Key Performance Indicator) & How to dramatically increase performance? \\

                \bottomrule

                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
                \label{tab:indicators}
            \end{longtable}

        More information on the indicators can be found
        in chapter 1 of 
        as well as \cite{florac1999,kaplan1992}.

@@

        It is important to note that software departments do not just
        develop software.  The department has many other duties
        including: deploying software, installing server hardware/software,
        writing documentation, surveying users, research, innovation,
        education and other common business duties.

@@

making decisions based upon historical data.

### 2015-02-23 paper_40_mpi.tex
working on Chapter 3

        \subsubsection{QUALITY}
            Measuring quality is a crucial part of accessing 
            software development results.  
            Poor quality means time, money, and resources are spent 
            fixing the problems. As a result, new features are not being
            created. One of the key indicators of software quality 
            is defects.  Thus, it is important
            to measure the number of defects associated with a software 
            release.  The following is the necessary data to collect
            and an algorithm to calculate
            the quality score of software being released.

@@

>>>>

        \subsubsection{QUALITY}
            Measuring quality is a crucial part of accessing 
            software development results.  
            Poor quality means time, money, and resources are spent 
            fixing the problems. As a result, new features are not being
            created. One of the key indicators of software quality 
            is defects.  It is important
            to measure the number of defects associated with a software 
            release because industry-wide the current defect removal rate is only 
            about 85\% and this value should be increased to 
            about 95\% for high quality software \cite{Jones2009}. 
            Organizations are leaving too many defects unfixed.  If organizations
            could lower the number of defects, then not as many defects would
            need to be fixed, which in turn would raise the defect removal rate.

            Another aspect of defects is severity levels.  A severity level indicates
            the importance of a defect that has been discovered.  Although an
            organization can choose whatever severity levels they choose, it is
            common practice to use 5 severity levels \cite{Raynus1999}.  The most 
            severe level for a defect is 1.  All other levels drop in severity 
            from that point. Table \ref{tab:severity} describes the 5 levels
            for defect severity.

            \begin{longtable}{@{}l l}
                \toprule%
                 \centering%
                 {\bfseries Level}
                 & {\bfseries Description}\\

                1 & Software is unavailable and no workaround   \\
                \myrowcolour%
                2 & Software performance degraded with no workaround \\
                3 & Software performance degraded but workaround exists \\
                \myrowcolour%
                4 & Software functions but a loss of non-critical functionality \\
                5 & Others: minor cosmetic issue, missing documentation \\

                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
                \label{tab:severity}
            \end{longtable}

@@

                Notice the data does not include a severity level.  The severity
                level should be handled before being stored.  A good technique is
                to count the defects based upon the weighting scheme
                in Table \ref{tab:severityweight} \cite{Raynus1999}. For
                example, finding 1 defect of severity level 5 will result
                in total count of 1.  However, finding 1 defect of severity
                level 2 will result in a total count of 15. This strategy helps
                to standardize the number of defects found.  An organization
                can alter the values of Table \ref{tab:severityweight} based 
                upon priorities or use a different technique if desired.  It
                is just important to get a standard, meaningful number for SIT defects,
                UAT defects, and PROD defects which manages severity appropriately.

                    \toprule%
                     \centering%
                     {\bfseries Severity Level}
                     & {\bfseries Weight} \\

                    1 & 30 \\
                    \myrowcolour%
                    2 &  15 \\
                    3 &  5 \\
                    \myrowcolour%
                    4 &  2 \\ 
                    5 &  1 \\

                    \caption{DEFECT SEVERITY LEVEL WEIGHTING}
                    \label{tab:severityweight}
                \end{longtable}
